\chapter{Proposed Work}

The goal of this research is to provide an interactive interface to the NOAA MS-PROD model so as to help fishermen, fisheries managers, and other stakeholders understand the implications of decisions, such as changing catch quotas for particular kinds of fishing activity---e.g., bottom trawling versus mid-water trawling.  From using our interactive interface, users should gain insights into:
\begin{itemize}
	\item \textbf{Implications of the model:}  E.g., how do two different sets of fishing effort values affect the biomass predictions of the ten species?
	\item \textbf{The model itself:}  E.g., why does the abundance of one species increase when another species is caught? 
\end{itemize}

Research for this thesis is being carried out in two phases, 1) a design and implementation phase and 2) an evaluation phase.  In the first phase, various design alternatives have been implemented with some feedback from the originators of the fisheries model (Robert Gamble in particular).  A substantial part of the research, particularly relating to design and implementation has already been completed; most of what remains is the evaluation component.  The following section discusses completed work and the section following that discusses work that remains to be done.%The first phase is almost completed, while the second phase has been planned but not carried out.

The following work is proposed for the completion of this masters thesis:

\begin{itemize}
  \item Visualization of change
  \item Visualization of inter-species relationships
  \item Visualization of uncertainty
  \item User evaluation
\end{itemize}

These are described in additional detail below.

\section{Visualization of Change}

In addition to the blended visualization of change mentioned in Section~\ref{sec:displayingChange}, we will introduce an alternative of the prior values represented simple curve without blending between the curves.

\section{Visualization of Inter-Species Relationships}

As described in Section~\ref{sec:betweenSpeciesArcs}, users can toggle between no interspecies arcs, predation arcs, and interaction arcs.  An alternative will be developed where arcs of both types appear only selectively---i.e., an arc representing the effect of ``Species A'' on ``Species B'' will only appear if some change in effort values resulted in the biomass of ``Species B'' changing.

\section{Visualization of Uncertainty}

The output of all scientific models is best understood as a range of expected values, since models are merely simplifications of reality.  Therefore, we will perform Monte Carlo simulations by randomly jittering the non-zero input parameter values $\pm 10\%$ for the MS-PROD model.  The resulting uncertainty will be displayed in one of the following methods:

 \begin{itemize}
   \item Multi-line (one semi-transparent line per Monte Carlo simulation run)
   \item Error bars of standard deviations
   \item Error bands of standard deviations
   \item Error boxes of quartiles
 \end{itemize}

\section{User Evaluation}

The user evaluation will be conducted in the manner of a semi-structured interview.  Users will be instructed on the various features of the MS-PROD visualization, then asked to either rate or rank the different features.  Some questions which may be included are:

\begin{itemize}
  \item Which visualization method did you like the best?
  \item How useful did you find this feature?
  \item How well do you think you have understood the model?
\end{itemize}
