\documentclass[11pt]{report}
\usepackage{unhthesis}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage[round]{natbib}
\usepackage{mathtools}
\usepackage{setspace}
\usepackage[table]{xcolor}

\usepackage{verbatimbox}

\usepackage[toc,page]{appendix}

\renewcommand{\citep}[1]{\citeauthor{#1}~(\citeyear{#1})}
\renewcommand{\cite}[1]{(\citeauthor{#1},~\citeyear{#1})}

\newcommand{\answerText}[2][red]{\textcolor{#1}{\textit{#2}}}

\makeatletter
\newcommand{\redub}{}
\def\redub#1{%
  \@ifnextchar_%
    {\@redub{#1}}
    {\@latex@warning{Missing argument for \string\redub}\@redub{#1}_{}}%
}
\def\@redub#1_#2{%
    \colorlet{currentcolor}{.}%
    \color{red}%
    \underbrace{\color{currentcolor}#1}_{\color{red}#2}%
    \color{currentcolor}%
}
\makeatother


\hyphenation{Hu-go}
%\hyphenation{Mi-s\'e-ra-bles}

\begin{document}


\title{Using Interactive Visualization to Enhance Understanding of a Fisheries Model}     % Your title
\author{Carmen Rose St.\ Jean}				   % Your name
\prevdegrees{B.S., University of New Hampshire, 2010}
\major{Computer Science}				   % Your new major
\degree{Master of Science}				   % Your new degree
\degreemonth{May}					   % When awarded.
\degreeyear{2014}					   %
\thesisdate{\today}					   % Date of document.
\DOCUMENTtype{THESIS}                          % or DISSERTATION
\Documenttype{Thesis}                          % or Dissertation
\documenttype{thesis}                          % or dissertation
\maketitle     
                                                        % APPROVAL PAGE
                                                        %======================
\supervisor{Colin Ware}{Professor of Computer Science}    % <- One of these
\committee{R. Daniel Bergeron}{Professor of Computer Science}     % <- As many as
\committee{Matthew Plumlee}{Affiliate Assistant Professor in Computer Science}    %    you need...
\makeapproval 

%\begin{dedication}                                      % Delete these
%    To Mom and Dad.                                     % if no dedication
%\end{dedication}                                        % page.


                                                        % ACK. PAGE
                                                        %======================
\begin{acknowledgments}
I would like to thank my advisor Colin Ware for the encouragement, mentoring, and patience throughout the entire journey of writing my thesis.  His insights and criticisms were valuable and inspirational to me over the last year.  I was able to grow as a researcher and a person because he believed in me.

I also want to thank my committee members, Dan Bergeron and Matthew Plumlee.  Both of them were helpful with their advice and kindness over the course of this thesis and also during my entire time at UNH.

I am deeply grateful to John Kelley and Jason Greenlaw for their support and guidance both during and beyond my nowCOAST time.  They helped me realize what I was capable of by providing me with challenging opportunities.

I owe my thanks to Phil Hatcher, for knowing I was capable of completing a master's degree before I did.  I would also like to express my appreciation to Mark Bochert for my year as his teaching assistant, where I learned a lot and had a great time.  Thank you also to Mezgeb for providing good company during this thesis endeavor.

Finally, I am indebted to my father, my mother, Uncle Roger, Danielle, Amanda, and Eric for getting me to where I am today.  Thank you especially to Chris, for encouraging me to go back to school and providing endless reassurance to me whenever I was overwhelmed.  Last but certainly not least, I would like to thank God for this opportunity and the good health, wisdom, and courage to complete it.

\end{acknowledgments}                                   %

                                                        % FOREWORD PAGE
%\begin{foreword}                                        %======================
%     This is the foreword.                              % Delete these if
%\end{foreword}                                          % no foreword page.

							%======================
\tableofcontents					% Always needed...}
%\listoftables						% Delete if no tables.
%\addcontentsline{toc}{section}{LIST OF TABLES}
\listoffigures						% Delete if no figures.
\addcontentsline{toc}{section}{LIST OF FIGURES}

% Abstract page
\include{abstract}

\include{intro}
\include{reqAndDesign}
\include{evaluation}
\include{conclusion}


\bibliographystyle{plainnat}

\bibliography{sources}

\begin{appendices}

\include{parameters}
\include{protocol}
\include{questions}
\include{gradingKey}
\include{consent}

\end{appendices}



\end{document}
